Cohort Level Analysis

### 2021-08-18 output_scripts/Cohort_level_analysis.Rmd
current updates

slides_plots <- FALSE
extra_plots <- FALSE

revision_plots <- TRUE
original_plots <- FALSE
### original plots for plots which are no longer needed, 
### revision plots are what required

# current_cohort <- 5

# don't write to this path
data_path <- "../output/revisions/lapl_check/prior_check/"
no_eta_3_data_path <- "../output/revisions/lapl_check/ident_check/"
no_eta_1_data_path <- "../output/revisions/lapl_check/ident_check_no_eta1/"

@@

library(here)
# library(rstan)
library(cmdstanr)
Sys.setenv(LOCAL_CPPFLAGS = "-march=corei7 -mtune=corei7")
options(mc.cores = parallel::detectCores())
library(tidyverse)
library(R.utils)
library(RColorBrewer)
library(fields)
library(posterior)
library(bayesplot)
library(viridis)
library(here)
library(compete)
library(colorspace)
source(paste(func_dir, "naiveRankHierarchy.R", sep = ""))
source(paste(func_dir, "expertRankHierarchy.R", sep = ""))
source(paste(func_dir, "cleanData.R", sep = ""))
source(paste(func_dir, "prepareDataStan.R", sep = ""))
source(paste(func_dir, "inferLatentMmhp.R", sep = ""))
source(paste(func_dir, "plotUtil.R", sep = ""))
source(paste(func_dir, "mmhp.R", sep = ""))
source(paste(func_dir, "uniHawkes.R", sep = ""))
source(paste(func_dir, "simulatePrediction.R", sep = ""))
source(paste(func_dir, "myGlicko.R", sep = ""))
source(paste(func_dir, "matrixPlotParameter.R", sep = ""))
source(paste(func_dir, "residualStructureScore.R", sep = ""))
source(paste(func_dir, "drawIntensity.R", sep = ""))
source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")

@@

```{r load rankings, echo=FALSE, results='hide', cache=TRUE}
full_data <- readRDS("../data/mice.RData")
# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45

@@

###
print_total_less_windows <- function(current_cohort) {
  cat(paste("Cohort ", current_cohort, "\n", sep = ""))
  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
  stan_input_lst <- prepareDataStan(current_cohort)

@@

  load(paste(data_path,
             cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",
             cohort_names[current_cohort],
             ".RData",
             sep = ""
  ))
  plot_cols <- col_df %>%
    filter(method %in% c(
      "C-HP",
      "C-DCHP",
      "C-MMHP"
    )) %>%
    pull(cols)
  all_data <- sim_cohort_mmhp %>%
    select(starts_with("eta") | starts_with("w_lam") |
             starts_with("beta")) %>%
    select(! ends_with("delta")) %>% 
    pivot_longer(everything()) %>%
    mutate(Model = "C-MMHP") %>%
    bind_rows(sim_cohort_dchp %>%
                select(starts_with("eta") |
                         starts_with("w_lam") |
                         starts_with("beta")) %>%
                select(!ends_with("delta")) %>% 
                select(!ends_with("detla")) %>% 
                pivot_longer(everything()) %>%
                mutate(Model = "C-DCHP")) %>% 
    bind_rows(sim_cohort_hp %>%
                select(starts_with("eta") |
                         starts_with("w_lam") |
                         starts_with("beta")) %>%
                select(!ends_with("delta")) %>% 
                pivot_longer(everything()) %>%
                mutate(Model = "C-HP"))
  all_data$Model <- factor(all_data$Model,
                           levels = c("C-HP", "C-DCHP", "C-MMHP"))
  comp_plot <- ggplot(all_data, aes(name, value, fill = Model)) +
    geom_boxplot() +
    scale_fill_manual(values = plot_cols) +
    labs(title = paste("Cohort ", current_cohort, sep = ""),
         subtitle = "Estimated Model Parameters") +
    # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.text.x = element_blank()) +
    facet_wrap(~name, scales = "free")
  print(comp_plot)
  ###
  ## same for gamma
  all_data <- sim_cohort_mmhp %>%
    select(starts_with("gamma")) %>%
    pivot_longer(everything()) %>%
    mutate(Model = "C-MMHP") %>%
    bind_rows(sim_cohort_dchp %>%
                select(starts_with("gamma")) %>%
                pivot_longer(everything()) %>%
                mutate(Model = "C-DCHP"))
  all_data$Model <- factor(all_data$Model,
                           levels = c("C-HP", "C-DCHP", "C-MMHP"))
  all_data$name <- factor(all_data$name, 
                          levels = paste0("gamma[",1:12,"]"))
  comp_plot <- ggplot(all_data, aes(name, value, fill = Model)) +
    geom_boxplot() +
    scale_fill_manual(values = plot_cols[2:3]) +
    labs(title = paste("Cohort ", current_cohort, sep = ""),
         subtitle = "Out Degree Parameters", y = "Out Degree") +
    theme(axis.text.x = element_blank()) +
    facet_wrap(~name, scales = "free")
  print(comp_plot)
  ###
  all_data <- sim_cohort_mmhp %>%
    select(starts_with("zeta") ) %>%
    pivot_longer(everything()) %>%
    mutate(Model = "C-MMHP") %>%
    bind_rows(sim_cohort_dchp %>%
                select(starts_with("zeta")) %>%
                pivot_longer(everything()) %>%
                mutate(Model = "C-DCHP"))
  all_data$Model <- factor(all_data$Model,
                           levels = c("C-HP", "C-DCHP", "C-MMHP"))
  all_data$name <- factor(all_data$name, 
                          levels = paste0("zeta[",1:12,"]"))
  comp_plot <- ggplot(all_data, aes(name, value, fill = Model)) +
    geom_boxplot() +
    scale_fill_manual(values = plot_cols[2:3]) +
    labs(title = paste("Cohort ", current_cohort, sep = ""),
         subtitle = "In Degree Parameters", y = "In Degree") +
    facet_wrap(~name, scales = "free")
    # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  print(comp_plot)
}

@@

## Cohort 1

```{r set_cohort}
current_cohort <- 1
```

@@

### Total Events less Number of Windows containing events ordered by I&SI

```{r total-events-less-active-windows, message=FALSE}
active_events <- total_events_active(current_cohort)
colnames(active_events) <- expert_rank_10[[current_cohort]]
rownames(active_events) <- expert_rank_10[[current_cohort]]
print(active_events)
```

@@

@@

@@

@@

@@

<!-- ## Cohort 2 -->

<!-- ```{r set_cohort-2} -->
<!-- current_cohort <- 2 -->
<!-- ``` -->

<!-- ### Total Events ordered by I&SI ranking -->

<!-- ```{r total-events_2, message=FALSE} -->
<!-- print_total_events(current_cohort) -->
<!-- ``` -->

<!-- ### Total Events less Number of Windows containing events ordered by I&SI -->

<!-- ```{r total-events-less-active-windows-c2, message=FALSE} -->
<!-- print_total_less_windows(current_cohort) -->
<!-- ``` -->

<!-- ### Inferred ranking, ordered by total interactions -->

<!-- ```{r all-4-models-c2, warning=FALSE} -->
<!-- rankings_by_total(current_cohort) -->
<!-- ``` -->

<!-- <!-- Similarly, here are the corresponding plots with the animals ranked by --> 
<!-- <!-- I&SI score instead. -->

<!-- ### Inferred ranking ordered by I&SI score -->

<!-- ```{r ranked-by-isi-c2} -->
<!-- rankings_by_isi(current_cohort) -->
<!-- ``` -->

<!-- ## C 3  -->

<!-- ```{r set_cohort-3} -->
<!-- current_cohort <- 3 -->
<!-- ``` -->

<!-- ### Total Events ordered by I&SI ranking -->

<!-- ```{r total-events_3, message=FALSE} -->
<!-- print_total_events(current_cohort) -->
<!-- ``` -->

<!-- ### Total Events less Number of Windows containing events ordered by I&SI -->

<!-- ```{r total-events-less-active-windows-c3, message=FALSE} -->
<!-- print_total_less_windows(current_cohort) -->
<!-- ``` -->

<!-- ### Inferred ranking, ordered by total interactions -->

<!-- ```{r all-4-models-c3, warning=FALSE} -->
<!-- rankings_by_total(current_cohort) -->
<!-- ``` -->

<!-- <!-- Similarly, here are the corresponding plots with the animals ranked by --> 
<!-- <!-- I&SI score instead. -->

<!-- ### Inferred ranking ordered by I&SI score -->

<!-- ```{r ranked-by-isi-c3} -->
<!-- rankings_by_isi(current_cohort) -->
<!-- ``` -->

<!-- ### Compare parameter estimates with/without eta_3 -->

<!-- ```{r plot-rankings-both-models-no-eta3-c3, message=FALSE} -->
<!-- ests_without_eta_3(current_cohort) -->
<!-- ``` -->

<!-- ### Compare parameter estimates with/without eta_1 -->

<!-- ```{r plot-rankings-both-models-no-eta-1-c3, message=FALSE} -->
<!-- ests_without_eta_1(current_cohort) -->
<!-- ``` -->

<!-- ## C 4 -->

<!-- ```{r set_cohort-4} -->
<!-- current_cohort <- 4 -->
<!-- ``` -->

<!-- ### Total Events ordered by I&SI ranking -->

<!-- ```{r total-events_4, message=FALSE} -->
<!-- print_total_events(current_cohort) -->
<!-- ``` -->

<!-- ### Total Events less Number of Windows containing events ordered by I&SI -->

<!-- ```{r total-events-less-active-windows-c4, message=FALSE} -->
<!-- print_total_less_windows(current_cohort) -->
<!-- ``` -->

<!-- ### Inferred ranking, ordered by total interactions -->

<!-- ```{r all-4-models-c4, warning=FALSE} -->
<!-- rankings_by_total(current_cohort) -->
<!-- ``` -->

<!-- <!-- Similarly, here are the corresponding plots with the animals ranked by --> 
<!-- <!-- I&SI score instead. -->

<!-- ### Inferred ranking ordered by I&SI score -->

<!-- ```{r ranked-by-isi-c4} -->
<!-- rankings_by_isi(current_cohort) -->
<!-- ``` -->

<!-- ### Compare parameter estimates with/without eta_3 -->

<!-- ```{r plot-rankings-both-models-no-eta3-c4, message=FALSE} -->
<!-- ests_without_eta_3(current_cohort) -->
<!-- ``` -->

<!-- ### Compare parameter estimates with/without eta_1 -->

<!-- ```{r plot-rankings-both-models-no-eta-1-c4, message=FALSE} -->
<!-- ests_without_eta_1(current_cohort) -->
<!-- ``` -->

<!-- ## C 5 -->

<!-- ```{r set_cohort-5} -->
<!-- current_cohort <- 5 -->
<!-- ``` -->

<!-- ### Total Events ordered by I&SI ranking -->

<!-- ```{r total-events_5, message=FALSE} -->
<!-- print_total_events(current_cohort) -->
<!-- ``` -->

<!-- ### Total Events less Number of Windows containing events ordered by I&SI -->

<!-- ```{r total-events-less-active-windows-c5, message=FALSE} -->
<!-- print_total_less_windows(current_cohort) -->
<!-- ``` -->

<!-- ### Inferred ranking, ordered by total interactions -->

<!-- ```{r all-4-models-c5, warning=FALSE} -->
<!-- rankings_by_total(current_cohort) -->
<!-- ``` -->

<!-- <!-- Similarly, here are the corresponding plots with the animals ranked by --> 
<!-- <!-- I&SI score instead. -->

<!-- ### Inferred ranking ordered by I&SI score -->

<!-- ```{r ranked-by-isi-c5} -->
<!-- rankings_by_isi(current_cohort) -->
<!-- ``` -->

<!-- ### Compare parameter estimates with/without eta_3 -->

<!-- ```{r plot-rankings-both-models-no-eta3-c5, message=FALSE} -->
<!-- ests_without_eta_3(current_cohort) -->
<!-- ``` -->

<!-- ### Compare parameter estimates with/without eta_1 -->

<!-- ```{r plot-rankings-both-models-no-eta-1-c5, message=FALSE} -->
<!-- ests_without_eta_1(current_cohort) -->
<!-- ``` -->

<!-- ## C 6 -->

<!-- ```{r set_cohort-6} -->
<!-- current_cohort <- 6 -->
<!-- ``` -->

<!-- ### Total Events ordered by I&SI ranking -->

<!-- ```{r total-events_6, message=FALSE} -->
<!-- print_total_events(current_cohort) -->
<!-- ``` -->

<!-- ### Total Events less Number of Windows containing events ordered by I&SI -->

<!-- ```{r total-events-less-active-windows-c6, message=FALSE} -->
<!-- print_total_less_windows(current_cohort) -->
<!-- ``` -->

<!-- ### Inferred ranking, ordered by total interactions -->

<!-- ```{r all-4-models-c6, warning=FALSE} -->
<!-- rankings_by_total(current_cohort) -->
<!-- ``` -->

<!-- <!-- Similarly, here are the corresponding plots with the animals ranked by --> 
<!-- <!-- I&SI score instead. -->

<!-- ### Inferred ranking ordered by I&SI score -->

<!-- ```{r ranked-by-isi-c6} -->
<!-- rankings_by_isi(current_cohort) -->
<!-- ``` -->

<!-- ### Compare parameter estimates with/without eta_3 -->

<!-- ```{r plot-rankings-both-models-no-eta3-c6, message=FALSE} -->
<!-- ests_without_eta_3(current_cohort) -->
<!-- ``` -->

<!-- ### Compare parameter estimates with/without eta_1 -->

<!-- ```{r plot-rankings-both-models-no-eta-1-c6, message=FALSE} -->
<!-- ests_without_eta_1(current_cohort) -->
<!-- ``` -->

<!-- ## C 7 -->

>>>>

## cache_options for individual output types here? maybe?
cache_table <- FALSE
cache_corr <- FALSE
cache_pars <- FALSE

# don't write to this path
data_path <- "../output/revisions/aug_run/"

options(digits = 3)

@@

library(here)
# library(rstan)
library(cmdstanr)
Sys.setenv(LOCAL_CPPFLAGS = "-march=corei7 -mtune=corei7")
options(mc.cores = parallel::detectCores())
library(tidyverse)
library(R.utils)
library(RColorBrewer)
library(fields)
library(posterior)
library(bayesplot)
library(viridis)
library(here)
library(corrplot)
library(compete)
library(kableExtra)
library(colorspace)
source(paste(func_dir, "naiveRankHierarchy.R", sep = ""))
source(paste(func_dir, "expertRankHierarchy.R", sep = ""))
source(paste(func_dir, "cleanData.R", sep = ""))
source(paste(func_dir, "prepareDataStan.R", sep = ""))
source(paste(func_dir, "inferLatentMmhp.R", sep = ""))
source(paste(func_dir, "plotUtil.R", sep = ""))
source(paste(func_dir, "mmhp.R", sep = ""))
source(paste(func_dir, "uniHawkes.R", sep = ""))
source(paste(func_dir, "simulatePrediction.R", sep = ""))
source(paste(func_dir, "myGlicko.R", sep = ""))
source(paste(func_dir, "matrixPlotParameter.R", sep = ""))
source(paste(func_dir, "residualStructureScore.R", sep = ""))
source(paste(func_dir, "drawIntensity.R", sep = ""))
source("https://gist.githubusercontent.com/jalapic/6ca3ece44bdcdc522bb735f183aa0ca0/raw/1a07f469eff08117121b6cbebcd22fb7569e3ee8/compete_extra.R")

@@

```{css, echo=FALSE, cache=FALSE}
.header-section-number {
  display: none;
}

body {
  counter-reset: counter-level-1;
}

h1:not(.title) {
  counter-increment: counter-level-1;
  counter-reset: counter-level-2;
}

h2 {
  counter-increment: counter-level-1;
  counter-increment: counter-level-2;
  # counter-reset: counter-level-3;
}

h2::before {
  counter-increment: counter-level-1;
}

h3 {
  counter-increment: counter-level-3;
  counter-increment: counter-level-2;
}

h3::before {
  content: counter(counter-level-2) " ";
}
```

```{r load rankings, echo=FALSE, results='hide'}
full_data <- readRDS("../data/mice.RData")
# A=c9, B=c10, C=c12, D=c15, E=c16, F=c17, G=c18, H=c37, I=c38. J=c45

@@

print_total_less_windows <- function(current_cohort) {
  cat(paste("Cohort ", current_cohort, "\n", sep = ""))
  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
  stan_input_lst <- prepareDataStan(current_cohort)

@@

  load(paste(data_path,
             cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",
             cohort_names[current_cohort],
             ".RData",
             sep = ""
  ))
  plot_cols <- col_df %>%
    filter(method %in% c(
      "C-HP",
      "C-DCHP",
      "C-MMHP"
    )) %>%
    pull(cols)
  all_data <- sim_cohort_mmhp %>%
    select(starts_with("eta") | starts_with("w_lam") |
             starts_with("beta")) %>%
    select(! ends_with("delta")) %>% 
    pivot_longer(everything()) %>%
    mutate(Model = "C-MMHP") %>%
    bind_rows(sim_cohort_dchp %>%
                select(starts_with("eta") |
                         starts_with("w_lam") |
                         starts_with("beta")) %>%
                select(!ends_with("delta")) %>% 
                select(!ends_with("detla")) %>% 
                pivot_longer(everything()) %>%
                mutate(Model = "C-DCHP")) %>% 
    bind_rows(sim_cohort_hp %>%
                select(starts_with("eta") |
                         starts_with("w_lam") |
                         starts_with("beta")) %>%
                select(!ends_with("delta")) %>% 
                pivot_longer(everything()) %>%
                mutate(Model = "C-HP"))
  all_data$Model <- factor(all_data$Model,
                           levels = c("C-HP", "C-DCHP", "C-MMHP"))
  w_lam_est <- all_data %>% 
    filter(name == "w_lambda") %>% 
    summarise(median(value)) %>% pull()
  comp_plot <- ggplot(all_data, aes(name, value, fill = Model)) +
    geom_boxplot() +
    scale_fill_manual(values = plot_cols) +
    labs(title = paste("Cohort ", current_cohort, sep = ""),
         subtitle = "Estimated Model Parameters") +
    # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
    theme(axis.text.x = element_blank()) +
    facet_wrap(~name, scales = "free")
  print(comp_plot)
  ###
  ## same for gamma
  all_data <- sim_cohort_mmhp %>%
    select(starts_with("gamma")) %>%
    pivot_longer(everything()) %>%
    mutate(Model = "C-MMHP",
           value = value * w_lam_est) %>%
    bind_rows(sim_cohort_dchp %>%
                select(starts_with("gamma")) %>%
                pivot_longer(everything()) %>%
                mutate(Model = "C-DCHP"))
  all_data$Model <- factor(all_data$Model,
                           levels = c("C-HP", "C-DCHP", "C-MMHP"))
  all_data$name <- factor(all_data$name, 
                          levels = paste0("gamma[",1:12,"]"))
  comp_plot <- ggplot(all_data, aes(name, value, fill = Model)) +
    geom_boxplot() +
    scale_fill_manual(values = plot_cols[2:3]) +
    labs(title = paste("Cohort ", current_cohort, sep = ""),
         subtitle = "Out Degree Parameters", y = "Out Degree") +
    theme(axis.text.x = element_blank()) +
    facet_wrap(~name, scales = "free")
  print(comp_plot)
  ###
  all_data <- sim_cohort_mmhp %>%
    select(starts_with("zeta") ) %>%
    pivot_longer(everything()) %>%
    mutate(Model = "C-MMHP",
           value = value * w_lam_est) %>%
    bind_rows(sim_cohort_dchp %>%
                select(starts_with("zeta")) %>%
                pivot_longer(everything()) %>%
                mutate(Model = "C-DCHP"))
  all_data$Model <- factor(all_data$Model,
                           levels = c("C-HP", "C-DCHP", "C-MMHP"))
  all_data$name <- factor(all_data$name, 
                          levels = paste0("zeta[",1:12,"]"))
  comp_plot <- ggplot(all_data, aes(name, value, fill = Model)) +
    geom_boxplot() +
    scale_fill_manual(values = plot_cols[2:3]) +
    labs(title = paste("Cohort ", current_cohort, sep = ""),
         subtitle = "In Degree Parameters", y = "In Degree") +
    facet_wrap(~name, scales = "free")
    # theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
  print(comp_plot)
}

fights_table <- function(current_cohort) {
  clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
  return_df <- cleanObservationPeriod(current_cohort,
                                      raw_df =
                                full_data[[cohort_names[current_cohort]]],
                                      clean_data
  )
  total_events <- clean_data$N_count
  active_events <- total_events_active(current_cohort)
  active_out <- rowSums(active_events)
  active_in <- colSums(active_events)
  out_fights <- rowSums(total_events)
  in_fights <- colSums(total_events)
  fight_data <- tibble(node = 1:12,
                       out_fights = out_fights,
                       in_fights = in_fights,
                       out_act_perc = active_out/out_fights,
                       in_act_perc = active_in/in_fights)

  isi_rank <- expert_rank_10[[current_cohort]]
  # this orders from best to worst
  ## load cmmhp rank
  load(paste(data_path,
             cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",
             cohort_names[current_cohort],
             ".RData",
             sep = ""
  ))
  cmmhp_rank <- sim_cohort_mmhp %>% 
    select(starts_with("f")) %>% 
    pivot_longer(everything()) %>% 
    group_by(name) %>% 
    summarise(cmmhp_rank = median(value))
  out_degrees <- sim_cohort_mmhp %>% 
    select(starts_with("gamma")) %>% 
    pivot_longer(everything()) %>% 
    group_by(name) %>% 
    summarise(out_degree = median(value)) %>% 
    mutate(node = stringr::str_extract(name,
                                       pattern = "[:digit:]+")) %>%
    mutate(node = as.integer(node)) %>% 
    select(node, out_degree)
  in_degrees <- sim_cohort_mmhp %>% 
    select(starts_with("zeta")) %>% 
    pivot_longer(everything()) %>% 
    group_by(name) %>% 
    summarise(in_degree = median(value)) %>% 
    mutate(node = stringr::str_extract(name,
                                       pattern = "[:digit:]+")) %>% 
    mutate(node = as.integer(node)) %>% 
    select(node, in_degree)
  cmmhp_names <- stringr::str_extract(cmmhp_rank$name,
                                      pattern = "[:digit:]+")
  cmmhp_ranks <- tibble(node = cmmhp_names, 
                        rank = cmmhp_rank$cmmhp_rank) %>% 
    arrange(desc(rank)) %>% 
    mutate(node = as.integer(node), num_rank_cmmhp = 1:12)
  isi_ranks <- tibble(node = isi_rank, 
                      num_rank_isi = 1:length(cmmhp_names))
  ## don't need isi or cmmhp ranks here

  summary_data <- fight_data %>% 
    left_join(cmmhp_ranks, by = "node") %>% 
    left_join(isi_ranks, by = "node") %>% 
    left_join(out_degrees, by = "node") %>% 
    left_join(in_degrees, by = "node") %>% 
    # this will
    mutate(isi_less_cmmhp = num_rank_isi - num_rank_cmmhp) %>% 
    select(-c(rank,num_rank_isi, num_rank_cmmhp)) %>% 
    pivot_longer(cols = out_fights:isi_less_cmmhp)

  # knitr::kable(summary_data)
  summary_data
}

corr_matrices <- function(current_cohort) {
  load(paste(data_path,
             cohort_names[current_cohort],
             "/cohort_mmhp_stan_result_",
             cohort_names[current_cohort],
             ".RData",
             sep = ""
  ))

  m3_ranks <- sim_cohort_mmhp %>% 
    select(starts_with("f")) %>% 
    pivot_longer(everything()) %>% 
    group_by(name) %>% 
    summarise("C-MMHP" = median(value))

  load(paste(data_path,
             cohort_names[current_cohort],
             "/cohort_hp_stan_result_",
             cohort_names[current_cohort],
             ".RData",
             sep = ""
  ))

  m1_ranks <- sim_cohort_hp %>% 
    select(starts_with("f")) %>% 
    pivot_longer(everything()) %>% 
    group_by(name) %>% 
    summarise("C-HP" = median(value))

  load(paste(data_path,
             cohort_names[current_cohort],
             "/cohort_dchp_stan_result_",
             cohort_names[current_cohort],
             ".RData",
             sep = ""
  ))

  m2_ranks <- sim_cohort_dchp %>% 
    select(starts_with("f")) %>% 
    pivot_longer(everything()) %>% 
    group_by(name) %>% 
    summarise("C-DCHP" = median(value))

  ranks <- m1_ranks %>% 
    left_join(m2_ranks, by = "name") %>% 
    left_join(m3_ranks, by = "name")

  cor_matrix <- cor(ranks[,2:4])
  # col3 = colorRampPalette(c('red', 'white', 'blue'))
  corrplot(cor_matrix,
           type = "upper",
           tl.col = "black",
           col.lim = c(0,1),
        title = "Pearson Correlation median ranks",
        mar = c(0, 0, 1, 0), diag = FALSE)

  ## same think for spearman rank correlation
  m1_num <- m1_ranks %>% 
    rename(value = "C-HP") %>% 
    arrange(desc(value)) %>% 
    mutate(chp = 1:12) %>% 
    mutate(node = stringr::str_extract(name,
                                       pattern = "[:digit:]+")) %>%
    mutate(node = as.integer(node)) %>% 
    select(node, chp)

  m2_num <- m2_ranks %>% 
    rename(value = "C-DCHP") %>% 
    arrange(desc(value)) %>% 
    mutate(cdchp = 1:12) %>% 
    mutate(node = stringr::str_extract(name,
                                       pattern = "[:digit:]+")) %>%
    mutate(node = as.integer(node)) %>% 
    select(node, cdchp)

  m3_num <- m3_ranks %>% 
    rename(value = "C-MMHP") %>% 
    arrange(desc(value)) %>% 
    mutate(cmmhp = 1:12) %>% 
    mutate(node = stringr::str_extract(name,
                                       pattern = "[:digit:]+")) %>%
    mutate(node = as.integer(node)) %>% 
    select(node, cmmhp)

  isi_ranks <- tibble(node = expert_rank_10[[current_cohort]],
                      isi = 1:12)
  ###
  rank_df <- m1_num %>% 
    left_join(m2_num, by = "node") %>% 
    left_join(m3_num, by = "node") %>% 
    left_join(isi_ranks, by = "node")

  spear_cor <- cor(rank_df[,2:5], method = "spearman")

  corrplot(spear_cor,
           type = "upper",
           tl.col = "black",
           col.lim = c(0,1),
           title = "Spearman Rank Correlation",
           mar = c(0, 0, 1, 0), diag = FALSE)
}
```

@@

## Cohort 1 {-}

```{r set_cohort}
current_cohort <- 1
clean_data <- cleanData(full_data[[cohort_names[current_cohort]]])
# the clean_data is handy for other intermediate analyses
```

@@

### Total Active Events ordered by I&SI

Here all events which are classified as inactive by the C-MMHP model
originate from the top ranked animal. As such there is strong
agreement between the win/loss matrix of all events and
those ocurring in active periods, with the 
restriction to only active events
slightly decreasing the 
influence of the top ranked animal.

```{r total-events-less-active-windows, message=FALSE}
active_events <- total_events_active(current_cohort)
active_events <- active_events[expert_rank_10[[current_cohort]],
                               expert_rank_10[[current_cohort]]]
colnames(active_events) <- expert_rank_10[[current_cohort]]
rownames(active_events) <- expert_rank_10[[current_cohort]]
print(active_events)
```

@@

Examing the correlation matrices of both the median ranks for
each of our cohort models and the Spearman rank correlations,
we see that the C-HP most agrees with the I&SI ranking,
with the C-DCHP and C-MMHP models showing progressively less agreement.

```{r corr-plots, message=FALSE}
corr_matrices(current_cohort)
```

@@

We next plot the inferred posterior rank estimates from 
each of our cohort models and the comparison AggRank model,
where we order the animals by the estimated I&SI ranking.

@@

Similarly, to show how this rank differs from that obtained by the C-MMHP
model, we order the animals by the inferred ranking from that
model.

@@

For each of our three proposed models, we show the parameter
estimates for the non rank parameters, including the in and
out degree estimates for the models which incorporate degree
corrections.

@@

### Summary Table

Finally, for each animal in this cohort, we summarise

```{r summ_tabls, message=FALSE}
c1_summ <- fights_table(current_cohort)
# c1_summ %>% 
#   kbl() %>% 
#   kable_styling()

c1_summ %>% 
  pivot_wider(id_cols = node) %>% 
  rename(out_deg = out_degree, in_deg = in_degree,
         "Out Events" = out_fights,
         "In Events" = in_fights,
         "% In Active" = in_act_perc, "% Out Active" = out_act_perc,
         "Out Degree" = out_degree,
         "In Degree" = in_degree,
         "I&SI to C-MMHP change" = isi_less_cmmhp,
         "Animal" = node) %>% 
  kbl() %>% 
  kable_styling()
```

## Cohort 2 {-}

```{r set_cohort2}
current_cohort <- 2
```

```{r total-events_2, message=FALSE}
print_total_events(current_cohort)
```

### Total Active Events ordered by I&SI

```{r total-events-less-active-windows2, message=FALSE}
active_events <- total_events_active(current_cohort)
active_events <- active_events[expert_rank_10[[current_cohort]],
                               expert_rank_10[[current_cohort]]]
colnames(active_events) <- expert_rank_10[[current_cohort]]
rownames(active_events) <- expert_rank_10[[current_cohort]]
print(active_events)
```

```{r corr-plots2, message=FALSE}
corr_matrices(current_cohort)
```

```{r ranked-by-isi2}
rankings_by_isi(current_cohort)
```

```{r ranked-by-cmmhp2}
rankings_by_cmmhp(current_cohort)
```

```{r param-ests2, message=FALSE}
param_ests(current_cohort)
```

### Summary Table

```{r summ_tabls2, message=FALSE}
c2_summ <- fights_table(current_cohort)

c2_summ %>% 
  pivot_wider(id_cols = node) %>% 
  rename(out_deg = out_degree, in_deg = in_degree,
         "Out Events" = out_fights,
         "In Events" = in_fights,
         "% In Active" = in_act_perc, "% Out Active" = out_act_perc,
         "Out Degree" = out_degree,
         "In Degree" = in_degree,
         "I&SI to C-MMHP change" = isi_less_cmmhp,
         "Animal" = node) %>% 
  kbl() %>% 
  kable_styling()
```

## Cohort 3 {-}

```{r set_cohort3}
current_cohort <- 3
```

```{r total-events_3, message=FALSE}
print_total_events(current_cohort)
```

### Total Active Events ordered by I&SI

```{r total-events-less-active-windows3, message=FALSE}
active_events <- total_events_active(current_cohort)
active_events <- active_events[expert_rank_10[[current_cohort]],
                               expert_rank_10[[current_cohort]]]
colnames(active_events) <- expert_rank_10[[current_cohort]]
rownames(active_events) <- expert_rank_10[[current_cohort]]
print(active_events)
```

```{r corr-plots3, message=FALSE}
corr_matrices(current_cohort)
```

```{r ranked-by-isi3}
rankings_by_isi(current_cohort)
```

```{r ranked-by-cmmhp3}
rankings_by_cmmhp(current_cohort)
```

```{r param-ests3, message=FALSE}
param_ests(current_cohort)
```

### Summary Table

```{r summ_tabls3, message=FALSE}
c3_summ <- fights_table(current_cohort)

c3_summ %>% 
  pivot_wider(id_cols = node) %>% 
  rename(out_deg = out_degree, in_deg = in_degree,
         "Out Events" = out_fights,
         "In Events" = in_fights,
         "% In Active" = in_act_perc, "% Out Active" = out_act_perc,
         "Out Degree" = out_degree,
         "In Degree" = in_degree,
         "I&SI to C-MMHP change" = isi_less_cmmhp,
         "Animal" = node) %>% 
  kbl() %>% 
  kable_styling()
```

## Cohort 4 {-}

```{r set_cohort4}
current_cohort <- 4
```

```{r total-events_4, message=FALSE}
print_total_events(current_cohort)
```

### Total Active Events ordered by I&SI

```{r total-events-less-active-windows4, message=FALSE}
active_events <- total_events_active(current_cohort)
active_events <- active_events[expert_rank_10[[current_cohort]],
                               expert_rank_10[[current_cohort]]]
colnames(active_events) <- expert_rank_10[[current_cohort]]
rownames(active_events) <- expert_rank_10[[current_cohort]]
print(active_events)
```

```{r corr-plots4, message=FALSE}
corr_matrices(current_cohort)
```

```{r ranked-by-isi4}
rankings_by_isi(current_cohort)
```

```{r ranked-by-cmmhp4}
rankings_by_cmmhp(current_cohort)
```

```{r param-ests4, message=FALSE}
param_ests(current_cohort)
```

### Summary Table

```{r summ_tabls4, message=FALSE}
c4_summ <- fights_table(current_cohort)

c4_summ %>% 
  pivot_wider(id_cols = node) %>% 
  rename(out_deg = out_degree, in_deg = in_degree,
         "Out Events" = out_fights,
         "In Events" = in_fights,
         "% In Active" = in_act_perc, "% Out Active" = out_act_perc,
         "Out Degree" = out_degree,
         "In Degree" = in_degree,
         "I&SI to C-MMHP change" = isi_less_cmmhp,
         "Animal" = node) %>% 
  kbl() %>% 
  kable_styling()
```

## Cohort 5 {-}

```{r set_cohort5}
current_cohort <- 5
```

```{r total-events_5, message=FALSE}
print_total_events(current_cohort)
```

### Total Active Events ordered by I&SI

```{r total-events-less-active-windows5, message=FALSE}
active_events <- total_events_active(current_cohort)
active_events <- active_events[expert_rank_10[[current_cohort]],
                               expert_rank_10[[current_cohort]]]

colnames(active_events) <- expert_rank_10[[current_cohort]]
rownames(active_events) <- expert_rank_10[[current_cohort]]
print(active_events)
```

```{r corr-plots5, message=FALSE}
corr_matrices(current_cohort)
```

```{r ranked-by-isi5}
rankings_by_isi(current_cohort)
```

```{r ranked-by-cmmhp5}
rankings_by_cmmhp(current_cohort)
```

```{r param-ests5, message=FALSE}
param_ests(current_cohort)
```

### Summary Table

```{r summ_tabls5, message=FALSE}
c5_summ <- fights_table(current_cohort)

c5_summ %>% 
  pivot_wider(id_cols = node) %>% 
  rename(out_deg = out_degree, in_deg = in_degree,
         "Out Events" = out_fights,
         "In Events" = in_fights,
         "% In Active" = in_act_perc, "% Out Active" = out_act_perc,
         "Out Degree" = out_degree,
         "In Degree" = in_degree,
         "I&SI to C-MMHP change" = isi_less_cmmhp,
         "Animal" = node) %>% 
  kbl() %>% 
  kable_styling()
```

## Cohort 6 {-}

```{r set_cohort6}
current_cohort <- 6
```

```{r total-events_6, message=FALSE}
print_total_events(current_cohort)
```

### Total Active Events ordered by I&SI

```{r total-events-less-active-windows6, message=FALSE}
active_events <- total_events_active(current_cohort)
active_events <- active_events[expert_rank_10[[current_cohort]],
                               expert_rank_10[[current_cohort]]]

colnames(active_events) <- expert_rank_10[[current_cohort]]
rownames(active_events) <- expert_rank_10[[current_cohort]]
print(active_events)
```

```{r corr-plots6, message=FALSE}
corr_matrices(current_cohort)
```
